quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-10 paper-quollr.Rmd
Updated Figure 3 adding the box

wireframe_scurve_int <- ggplotly(wireframe_scurve, 
                                width = "350", 
                                height = "320", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

>>>>

wireframe_scurve_int <- plot_ly() |>
    # Wireframe segments
    add_segments(
        data = tr_from_to_df_scurve,
        x = ~x_from, y = ~y_from,
        xend = ~x_to, yend = ~y_to,
        line = list(color = "#000000", width = 0.5),
        hoverinfo = "none",
        showlegend = FALSE
    ) |>
    # Centroid points
    add_markers(
        data = df_bin_centroids_scurve,
        x = ~c_x, y = ~c_y,
        marker = list(size = 4, color = "#FF7755"),
        hoverinfo = "none",
        showlegend = FALSE
    ) |>
    # Layout with border
    layout(
        width = 350,
        height = 320,
        xaxis = list(
            range = sc_xlims,
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            title = ""
        ),
        yaxis = list(
            range = sc_ylims,
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            title = ""
        ),

        # ADD A BOX AROUND THE ENTIRE PLOT PANEL
        shapes = list(
            list(
                type = "rect",
                xref = "paper", yref = "paper",
                x0 = 0, y0 = 0,
                x1 = 1, y1 = 1,
                line = list(color = "black", width = 1)
            )
        )
    ) |>
    config(
        staticPlot = TRUE,
        displayModeBar = FALSE,
        editable = FALSE,
        showTips = FALSE,
        displaylogo = FALSE,
        responsive = FALSE
    )
